An Integral-field Spectroscopic Study of Low-power Radio Galaxies

### 2020-09-23 paper.tex
Tweeks to Halpha/beta profiles
Improved refs and discussion of galaxies re ISM

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert.}}

@@

There is a strong consensus in the literature that the most powerful
radio galaxies are the result of gas-rich major mergers, that cause
large amounts of material to fall on to the black hole at the centre
of the resulting galaxy, thus producing an immensely powerful AGN that
includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992,
  Lim2000}. However, such galaxies are extremely rare and are not
representative of the general radio galaxy population. Most radio
galaxies are low powered, and their basic properties and origins are
poorly constrained. One of the most popular suggestions is that they
are bona-fide detections of jet-mode AGN \citep[e.g.][]{Heckman2014}.
% , a class of AGN thought to maintain the dearth of star formation in
% early-type galaxies (ETGs), after most of the fuel for star
% formation has been removed by an earlier event.
These low-power radio galaxies are known to be dusty, the dust lanes
having a tendency to be perpendicular to the jets
\citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little
ionised gas \citep[e.g.][]{Sarzi2005}, but often have significant
quantities of hot X-ray gas \citep[e.g.][]{Canizares1987}. The
molecular ISM of our sample galaxies has already been examined in
\citet{ruffa2019, ruffa2020}. If the low star-formation rates
typically seen in massive ETGs are preserved by jet-mode AGN, then all
these ETGs must regularly go through similarly active phases, and
therefore low-power radio galaxies should be much the same as their
radio-quiet (quiescent phase) ETG counterparts.

@@

Our Southern Sample was initially observed with the Atacama Pathfinder
Experiment \citep[APEX; ][]{Gusten2006}, with a detection claimed in
the \ce{^{12}CO(2-1)} transition for every galaxy
\citep{Prandoni2012}. Some galaxies had an extremely large line width
(up to a full width at half-maximum of $904$~km~s$^{-1}$ for IC~4296),
but most showed a flat or double-horn spectrum suggestive of ordered
rotation. Follow-up Atacama Large Millimeter/sub-millimeter Array
(ALMA) observations were recently presented in \citet{ruffa2019,
  ruffa2020}.

@@

Each emission line is removed from each spectrum by subtracting the
best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
data, before the line strenghts are measured. \removed{, using only the 
stellar templates (and continuum correction) subsequently considered 
for the velocity dispersion correction (see below). \mbox{\textbf{(I do not 
understand the second part of this sentence. Check/clarify/correct.)}}} 
These are then corrected for the effects of the stellar velocity 
dispersion, as detailed below.
% used for reconstructing the best-fit to

@@

{\bf (Why not do a test here as in the next
  Sub-section~\ref{subsec:FR-SR} but for the RR/NRR classification,
  i.e.\ taking into account the mass differences of the two samples? I
  suggest you do, and then move the description of that test to this
  (first) sub-section. You then need not repeat the test description
  in Sub-section~\ref{subsec:FR-SR}; just state the results.)}

@@

{\bf (A solution to these large $PA_\text{phot}$ uncertainties would
  be to measure $PA_\text{phot}$ not from the surface brightness maps
  reconstructed from the IFS data, but rather from actual images, of
  which there should be many easily available. Of course, you would
  then need to make sure you know the orientation of these images
  accurately. Try it?)}

@@

Part of the red continuum band of the Mg$_2$ index is outside the
spectral range of VIMOS, but \citet{Ziegler1997} showed there is an
approximately linear relationship between Mg~$b$ and Mg$_2$, with a
gradient of $14.3$\,--\,$15.5$~mag~\AA$^{-1}$ depending on
metallicity. {\bf (Why the strange units? Is Mg$_2$ measured in mag 
rather than \AA? If so, add a short note. If not, correct.)} 
\added{(Mg$_2$ is condered to be a molecular index and is thus measured 
in units of mag$^{-1}$.) We can thus}\removed{Thus, following \citet{Ziegler1997}, we also} use Mg~$b$ as a proxy for
Mg$_2$.

@@

{\bf (One element I find confusing in this sub-section is that the
  first paragraph mentions a ``global'' relation, but the third
  paragraph and Fig.~3 use central $2\arcsec$ radius apertures that
  are therefore ``central'' apertures. Which one is right? You need to
  harmonise this. Also, in Fig.~\ref{fig:globalMg}, are you using the
  full relation of \citet{Ziegler1997} or just their gradient (and you
  then select a zero-point that suits you)? If the latter, then you
  must state this in the text. In other words, is the near perfect
  match of the green dashed and blue dotted lines truly a result or is
  it partially by construction (i.e.\ because you matched the
  zero-points yourself)? Clarify.) JW: the entire function has been transformed including the zero-point. This actually results in a cubic function (see Appendix A of \citealt{Vazdekis2010}), though as can been seen from the Fig.~3, the quadradic and cubic terms have very little effect in this range.}

@@

Table \ref{tab:litAbsorption} summarises our comparisons to multiple
sets of literature measurements, where the offsets and dispersions
listed are defined as the means and standard deviations of the
differences between the literature measurements and ours. For the
comparison to \citet{Vazdekis2010}, we re-analysed the Spectral Aeral
Unit for Research on Optical Nebulae (SAURON)
dataset\footnote{\url{http://www.strw.leidenuniv.nl/sauron/}}
\citep{Emsellem2004} using the same analysis pipeline as for our
Southern Sample. {\bf (Why not use the much larger Atlas$^{\rm 3D}$
  dataset instead? Explain briefly if justified.)} \added{This was used over the larger Atlas$^\text{3D}$ sample \citep{Cappellari2011}, as stellar populations were not published by the Atlas$^\text{3D}$ team.}

@@

\added{\textbf{IC~1459} has ionised gas co-rotating with the outer part (not the KDC) of the host galaxy \citep{Franx1988}. Whilst this is consistent with an internal origin of the gas, it should be noted that a major merger is typically expected to deplete a galaxy's gas reservoir. Either this did not happen in this case (a major merger being evidenced by the existence of the KDC) or the ISM may has an external origin and the apparent alignment of the gas and outer stars is random.}

\textbf{NGC~612} has well aligned stellar and ionised gas kinematics
(see Fig.~\ref{fig:ngc612}), the misalignment angle (measured as
described in Section~\ref{subsubsec:KinPA}) being just
$1\fdg0\pm0\fdg7$, thus consistent with an internal gas origin. This
adds to the evidence {\bf (What is the other evidence?
  Summarise/quote it or rephrase.)} that NGC~612 has not undergone a
recent major merger (major mergers exhaust galaxies of their gas and
destroy stellar discs), suggesting in turn that the fuelling of the
radio jet could be a purely secular process.

%**********************************************************************
%This plot no longer exists... Which plot?!
%**********************************************************************

\textbf{NGC~1316} is a complex object. The existence of redshifted
emission lines with respect to the rest frame of the galaxy on both
sides of the galaxy shows the gas is not in a settled disc and there
must be some inflows/outflows. Even from a visual inspection of the
ionised gas velocity field (see Fig.~\ref{fig:ngc1316}), it is clear
that a simple exponential disc model will not fit the data well. We
instead speculate that that the high-velocity peak to the South-West
of the centre is an inflow towards the nucleus, {\bf (Is there any
  evidence for this? If so, state them!)} almost perpendicular to the
radio jet, although other interpretations are possible. Better quality
data (better $S/N$ and a wider field of view) coupled with more
sophisticated models are required to test this interpretation.
% Nevertheless, it is clear that the gas in not in a settled disc.

@@

\textbf{NGC~3100} has an interesting ISM morphology. The
\ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
maps in \removed{white} \added{cyan}; see Fig.~\ref{fig:ngc3100}) 
{\bf (Again, no white
  contours in the figure... pale blue/turquoise contours?)} show a
broken ring, the radio jet passing through the gaps, hence suggesting
a jet-ring interaction \citep[see][]{ruffa2019, ruffa2020}. The
ionised gas is brightest in those same gaps, that we interpret as
additional excitation of the gas due to shocks from the impact of the
jet. It is unclear if the ionised gas kinematics supports this
interpretation, being completely different than that of the stars (and
nearly totally blueshifted). The centre of rotation of the gas also
appears to be offset from the centre of the galaxy (as defined by its
stellar surface brightness), by several arcseconds to the west. {\bf
  (I really do not understand how you can identify a centre of
  rotation when there is no evidence of organised rotation at
  all. Either convince me of that or remove/change that
  comment. Perhaps mention the lack of obvious large-scale rotation
  instead?!)}

@@

\begin{figure}
  \centering \includegraphics[width=\columnwidth]{Halpha_profile.png}
  \caption{H$\alpha$ flux radial profiles derived from the MUSE
    data. Solid red lines show radial profiles proportional to
    $r^{-2}$, convolved with a Gaussian of width equal to the measured
    PSF. {\bf (But what about the zero-points of the red profiles? How
      are these set? Explain.)} {\bf (Make the axis labels and galaxy
      names as thick as the plot boxes.) {\bf (All labels are rather
        small. Enlarge?)} {\bf (Note that the bounding boxes of
        Figs.~5 and 6 are really bad (much too big), so that the
        ``width='' commands are useless. Please make sure {\em all}
        your bounding boxes are as tight as possible around the
        figures themselves.)}}
    \label{fig:Ha_profile_MUSE}}
\end{figure}

@@

\begin{figure*}
  \centering
  % \includegraphics[width=\textwidth]{eso443-g024.png}
  \caption{Spatially-resolved map of all the parameters derived from
    the VIMOS observations of ESO~443-G24. Each parameter is indicated
    in the top-left corner of each panel, and the colour scale limits
    are listed in the bottom-right corner of each panel. {\bf (Why are
      these not perfect fits to the bottom-right corners? Fix?)} The
    surface brightness (isophotes) are overlaid as black contours in
    all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
    overlaid in \removed{white} \added{cyan} {\bf (Pale blue or 
    turquoise? Correct.)} and the
    radio continuum contours from the VLA are overlaid in green. The
    radio band displayed depends on the data and angular resolution
    available \citep[see][]{ruffa2019, ruffa2020}. {\bf
      (``Metalicity'' should be ``Metallicity''. Also explain the
      meaning of the pale and dark greys bins.)}}
      % Preferable to rotate the colour table by $180$ deg, to match
      % the colour to the sense of the limits indicated in the
      % bottom-right corner of each plot?
  \label{fig:eso443}
\end{figure*}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert. JW: not deliberate - I'd left this to ask you about who to include.}}

@@

There is a strong consensus in the literature that the most powerful
radio galaxies are the result of gas-rich major mergers, that cause
large amounts of material to fall on to the black hole at the centre
of the resulting galaxy, thus producing an immensely powerful AGN that
includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992,
  Lim2000}. However, such galaxies are extremely rare and are not
representative of the general radio galaxy population. Most radio
galaxies are low powered, and their basic properties and origins are
poorly constrained. One of the most popular suggestions is that they
are bona-fide detections of jet-mode AGN \citep[e.g.][]{Heckman2014}.
% , a class of AGN thought to maintain the dearth of star formation in
% early-type galaxies (ETGs), after most of the fuel for star
% formation has been removed by an earlier event.
These low-power radio galaxies are known to be dusty, the dust lanes
having a tendency to be perpendicular to the jets
\citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little
ionised gas \citep[e.g.][]{Sarzi2005}, but often have significant
quantities of hot X-ray gas \citep[e.g.][]{Canizares1987}. The
molecular ISM of our sample galaxies has already been examined in
\citet{ruffa2019a, ruffa2019b}. If the low star-formation rates
typically seen in massive ETGs are preserved by jet-mode AGN, then all
these ETGs must regularly go through similarly active phases, and
therefore low-power radio galaxies should be much the same as their
radio-quiet (quiescent phase) ETG counterparts.

@@

Our Southern Sample was initially observed with the Atacama Pathfinder
Experiment \citep[APEX; ][]{Gusten2006}, with a detection claimed in
the \ce{^{12}CO(2-1)} transition for every galaxy
\citep{Prandoni2012}. Some galaxies had an extremely large line width
(up to a full width at half-maximum of $904$~km~s$^{-1}$ for IC~4296),
but most showed a flat or double-horn spectrum suggestive of ordered
rotation. Follow-up Atacama Large Millimeter/sub-millimeter Array
(ALMA) observations were recently presented in \citet{ruffa2019a,
  ruffa2019b}.

@@

Each emission line is removed from each spectrum by subtracting the
best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
data, before the line strengths are measured. \removed{, using only the 
stellar templates (and continuum correction) subsequently considered 
for the velocity dispersion correction (see below). \mbox{\textbf{(I do not 
understand the second part of this sentence. Check/clarify/correct.)}}} 
These are then corrected for the effects of the stellar velocity 
dispersion, as detailed below.
% used for reconstructing the best-fit to

@@

{\bf (Why not do a test here as in the next
  Sub-section~\ref{subsec:FR-SR} but for the RR/NRR classification,
  i.e.\ taking into account the mass differences of the two samples? I
  suggest you do, and then move the description of that test to this
  (first) sub-section. You then need not repeat the test description
  in Sub-section~\ref{subsec:FR-SR}; just state the results.) JW: Massive did not classify into RR/NRR and only using Altas3d doesn't cover the mass range sufficiently.}

@@

{\bf (A solution to these large $PA_\text{phot}$ uncertainties would
  be to measure $PA_\text{phot}$ not from the surface brightness maps
  reconstructed from the IFS data, but rather from actual images, of
  which there should be many easily available. Of course, you would
  then need to make sure you know the orientation of these images
  accurately. Try it?) JW: I going to leave this one: this is taking a long time for not a lot of gain. We don't place much weight on the PA in the conclusions given the small sample size.}

@@

Part of the red continuum band of the Mg$_2$ index is outside the
spectral range of VIMOS, but \citet{Ziegler1997} showed there is an
approximately linear relationship between Mg~$b$ and Mg$_2$, with a
gradient of $14.3$\,--\,$15.5$~mag~\AA$^{-1}$ depending on
metallicity. {\bf (Why the strange units? Is Mg$_2$ measured in mag 
rather than \AA? If so, add a short note. If not, correct.)} 
\added{(Mg$_2$ is considered to be a molecular index and is thus measured 
in units of mag$^{-1}$.) We can thus}\removed{Thus, following \citet{Ziegler1997}, we also} use Mg~$b$ as a proxy for
Mg$_2$.

@@

{\bf (One element I find confusing in this sub-section is that the
  first paragraph mentions a ``global'' relation, but the third
  paragraph and Fig.~3 use central $2\arcsec$ radius apertures that
  are therefore ``central'' apertures. Which one is right? You need to
  harmonise this. Also, in Fig.~\ref{fig:globalMg}, are you using the
  full relation of \citet{Ziegler1997} or just their gradient (and you
  then select a zero-point that suits you)? If the latter, then you
  must state this in the text. In other words, is the near perfect
  match of the green dashed and blue dotted lines truly a result or is
  it partially by construction (i.e.\ because you matched the
  zero-points yourself)? Clarify.) JW: the entire function has been transformed including the zero-point. This actually results in a cubic function (see Appendix A of \citealt{Vazdekis2010}), though as can been seen from the Fig.~3, the quadratic and cubic terms have very little effect in this range.}

@@

Table \ref{tab:litAbsorption} summarises our comparisons to multiple
sets of literature measurements, where the offsets and dispersions
listed are defined as the means and standard deviations of the
differences between the literature measurements and ours. For the
comparison to \citet{Vazdekis2010}, we re-analysed the Spectral Aerial
Unit for Research on Optical Nebulae (SAURON)
dataset\footnote{\url{http://www.strw.leidenuniv.nl/sauron/}}
\citep{Emsellem2004} using the same analysis pipeline as for our
Southern Sample. {\bf (Why not use the much larger Atlas$^{\rm 3D}$
  dataset instead? Explain briefly if justified.)} \added{This was used over the larger Atlas$^\text{3D}$ sample \citep{Cappellari2011}, as stellar populations were not published by the Atlas$^\text{3D}$ team.}

@@

\added{\textbf{IC~1459} has ionised gas co-rotating with the outer part (not the KDC) of the host galaxy \citep{Franx1988}. Whilst this is consistent with an internal origin of the gas, it should be noted that a major merger is typically expected to deplete a galaxy's gas reservoir. Either this did not happen in this case (a major merger being evidenced by the existence of the KDC) or as speculated by \citet{Prichard2019}, the observed result of IC~1459 is the product of multiple events e.g. the ISM may have an external origin and the apparent alignment of the gas and outer stars is random.}

\textbf{NGC~612} has well aligned stellar and ionised gas kinematics
(see Fig.~\ref{fig:ngc612}; \citealt{Goss1980}), the misalignment angle (measured as
described in Section~\ref{subsubsec:KinPA}) being just
$1\fdg0\pm0\fdg7$, thus consistent with an internal gas origin. This
adds to the evidence {\bf (What is the other evidence?
  Summarise/quote it or rephrase.)} that NGC~612 has not undergone a
recent major merger (major mergers exhaust galaxies of their gas and
destroy stellar discs), suggesting in turn that the fuelling of the
radio jet could be a purely secular process \citep{Ekers1978}.

\textbf{NGC~1316} is a complex object. The existence of redshifted
emission lines with respect to the rest frame of the galaxy on both
sides of the galaxy shows the gas is not in a settled disc and there
must be some inflows/outflows. Even from a visual inspection of the
ionised gas velocity field (see Fig.~\ref{fig:ngc1316}), it is clear
that a simple exponential disc model will not fit the data well. \added{\citet{Schweizer1980} noted that the projected axes of stellar and gas components are roughly perpendicular pointing to an external origin to the ISM \citep{Shklovskii1962}. Unfortunately we do not achieve a high enough $S/N$ to investigate the ionised gas in these regions.} \removed{We
instead speculate that that the high-velocity peak to the South-West
of the centre is an inflow towards the nucleus, {\bf (Is there any
  evidence for this? If so, state them!)} almost perpendicular to the
radio jet, although other interpretations are possible.} Better quality
data (better $S/N$ and a wider field of view) coupled with more
sophisticated models are required to \removed{test this interpretation.}\added{interpret this data.}
% Nevertheless, it is clear that the gas in not in a settled disc.

@@

\textbf{NGC~3100} has an interesting ISM morphology. The
\ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
maps in \removed{white} \added{cyan}; see Fig.~\ref{fig:ngc3100}) 
{\bf (Again, no white
  contours in the figure... pale blue/turquoise contours?)} show a
broken ring, \added{with} the radio jet passing through the gaps\removed{, hence suggesting}\added{. This suggests }
a jet-ring interaction \citep[see][]{ruffa2019a, ruffa2019b}. The
ionised gas is brightest in those same gaps, that we interpret as
additional excitation of the gas due to shocks from the impact of the
jet. It is unclear if the ionised gas kinematics supports this
interpretation, being completely different than that of the stars (and
nearly totally blueshifted). \removed{The centre of rotation of the gas also
appears to be offset from the centre of the galaxy (as defined by its
stellar surface brightness), by several arcseconds to the west.} \added{What is clear, is that there is a complete lack of any large-scale rotation of the ISM.} {\bf
  (I really do not understand how you can identify a centre of
  rotation when there is no evidence of organised rotation at
  all. Either convince me of that or remove/change that
  comment. Perhaps mention the lack of obvious large-scale rotation
  instead?!)}

@@

\begin{figure}
  \centering \includegraphics[width=\columnwidth]{Halpha_profile.png}
  \caption{H$\alpha$ flux radial profiles derived from the MUSE
    data. Solid red lines show radial profiles proportional to
    $r^{-2}$, convolved with a Gaussian of width equal to the measured
    PSF. \added{The fitting of these lines was done by eye.}{\bf (But what about the zero-points of the red profiles? How
      are these set? Explain.)} {\bf (Make the axis labels and galaxy
      names as thick as the plot boxes.) {\bf (All labels are rather
        small. Enlarge?)} {\bf (Note that the bounding boxes of
        Figs.~5 and 6 are really bad (much too big), so that the
        ``width='' commands are useless. Please make sure {\em all}
        your bounding boxes are as tight as possible around the
        figures themselves.)}}
    \label{fig:Ha_profile_MUSE}}
\end{figure}

@@

\begin{figure*}
  \centering
  % \includegraphics[width=\textwidth]{eso443-g024.png}
  \caption{Spatially-resolved map of all the parameters derived from
    the VIMOS observations of ESO~443-G24. Each parameter is indicated
    in the top-left corner of each panel, and the colour scale limits
    are listed in the bottom-right corner of each panel. {\bf (Why are
      these not perfect fits to the bottom-right corners? Fix?)} The
    surface brightness (isophotes) are overlaid as black contours in
    all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
    overlaid in \removed{white} \added{cyan} {\bf (Pale blue or 
    turquoise? Correct.)} and the
    radio continuum contours from the VLA are overlaid in green. The
    radio band displayed depends on the data and angular resolution
    available \citep[see][]{ruffa2019a, ruffa2019b}. {\bf
      (``Metalicity'' should be ``Metallicity''. Also explain the
      meaning of the pale and dark greys bins.)}}
      % Preferable to rotate the colour table by $180$ deg, to match
      % the colour to the sense of the limits indicated in the
      % bottom-right corner of each plot?
  \label{fig:eso443}
\end{figure*}
